A Dependently Typed Multi-Stage Calculus

### 2019-08-14 main.tex
Fix typos of reviewer 2.

	We study a dependently typed extension of a multi-stage programming language
\`a la MetaOCaml, which supports quasi-quotation and cross-stage persistence
for manipulation of code fragments as first-class values and an evaluation
construct for execution of programs dynamically generated by this code
manipulation. Dependent types are expected to bring to multi-stage
programming enforcement of strong invariants---beyond simple type safety---on
the behavior of dynamically generated code. An extension is, however, not
trivial because a type system would have to take stages---roughly speaking,
the number of surrounding quotations---of types into account.

To rigorously study properties of such an extension, we develop \LMD, which
is an extension of Hanada and Igarashi's typed calculus \LTP with dependent
types, and prove its properties including preservation, confluence, strong
normalization for full reduction, and progress for staged reduction.
Motivated by code generators such that the type of generated code depends on
a value from outside of quotations, we argue the significance of cross-stage
persistence in dependently typed multi-stage programming and certain type
equivalence that are not directly derived from reduction rules.

>>>>

	We study a dependently typed extension of a multi-stage programming language
\`a la MetaOCaml, which supports quasi-quotation and cross-stage persistence
for manipulation of code fragments as first-class values and an evaluation
construct for execution of programs dynamically generated by this code
manipulation. Dependent types are expected to bring to multi-stage
programming enforcement of strong invariants---beyond simple type safety---on
the behavior of dynamically generated code. An extension is, however, not
trivial because such a type system would have to take stages of types ---roughly speaking,
the number of surrounding quotations---into account.

To rigorously study properties of such an extension, we develop \LMD, which
is an extension of Hanada and Igarashi's typed calculus \LTP with dependent
types, and prove its properties including preservation, confluence, strong
normalization for full reduction, and progress for staged reduction.
Motivated by code generators that generate code whose type depends on
a value from outside of the quotations, we argue the significance of cross-stage
persistence in dependently typed multi-stage programming and certain type
equivalence that are not directly derived from reduction rules.
